Demystifying the Combination of Dynamic Slicing and \\ Spectrum-based Fault Localization

### 2019-02-25 paper/ijcai/paper.tex
updating table 5

Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
popular automated fault localization techniques. Spectrum-based fault
localization (\sfl{}) is amongst the most common statistical fault localization
technique used to rank faulty components
~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
This technique uses tests coverage information to rank program's components.
\Rui{this sentence does not belong to rw (We suspect...)-->} We
suspect that several highly suspicious components—often involved in failing, but
seldom in passing test runs—may be unrelated to the bug.

coPrior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques. \Rui{not related work. more of motivation (avoid words such as believe)-->}
Although, \ds{} does not ensure the improvement of \sfl{} since it
can remove faulty statements from the failing test, we believe it has a great
potential to help reducing test cases and improve \sfl{} accuracy. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.

>>>>

Statistics-based techniques (e.g., ~\cite{Pearson:2017:EIF:3097368.3097441}) are
popular automated fault localization techniques. Spectrum-based fault
localization (\sfl{}) is amongst the most common statistical fault localization
technique used to rank faulty components
~\cite{7390282,DBLP:conf/kbse/JonesH05,DBLP:journals/smr/LuciaLJTB14,DBLP:journals/jss/AbreuZGG09}.
This technique uses tests coverage information to rank program's components.

\Rui{this sentence does not belong to rw (We suspect...)-->} We
suspect that several highly suspicious components—often involved in failing, but
seldom in passing test runs—may be unrelated to the bug.

Prior work has investigated the \ds{}-\sfl{}
combination~\cite{Wotawa:2010:FLB:1848650.1849235,Alves:2011:FUD:2190078.2190115,DBLP:conf/ecai/HoferW12,lei-mao-dai-wang-2012,slicing-sfl-repair,christi2018reduce}.
Overall, these studies reported promissing results but based their conclusions
on a very small group of (mostly artificial) faults and using different
techniques.

\Rui{not related work. more of motivation (avoid words such as believe)-->}
Although, \ds{} does not ensure the improvement of \sfl{} since it
can remove faulty statements from the failing test, we believe it has a great
potential to help reducing test cases and improve \sfl{} accuracy. In this
study, a larger set of faults is evaluated and a more rigorous experimental
methodology.
